### 2020-09-01 paper/perfectGraphs.tex

To proove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.

@@

Below we will proove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one. The proof of the correctness of the other possible result is more complicated, see section 4 and theorem 5.1 of \cite{MC05}.

@@

	Now, since $x_1$, $x_2$ are nonadjacent $i \geq 2$. But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, that is $j \geq i$. So we get $i=j$. Let us choose $i$ minumum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
\end{proof}

>>>>

To prove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.

@@

Below we will prove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one. The proof of the correctness of the other possible result is more complicated, see section 4 and theorem 5.1 of \cite{MC05}.

@@

	Now, since $x_1$, $x_2$ are nonadjacent $i \geq 2$. But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, that is $j \geq i$. So we get $i=j$. Let us choose $i$ minimum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
\end{proof}

\subsection{Summary}

\TODO{todo?}
